\documentclass[letterpaper]{deedy-resume} 
\usepackage{fixltx2e}
\usepackage{hyperref}
\usepackage{color}
\usepackage[document]{ragged2e}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\begin{flushleft}
\Huge \color{gray} \textbf{Siddhartha}  \Huge \textbf{Nayak}\\*
\begin{small}
\color{darkgray} \textbf{2018csb1125 |} \color{gray} (+91) 9022249359 \\
\end{small}
\end{flushleft}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.29\textwidth} 

\section{Education} 

\subsection{IIT ROPAR}

\descript{BTech IN COMPUTER SCIENCE}
\location{2018-CURRENT }

\sectionspace 

\subsection{SARVODAYA SCHOOL}
\LOCATION{May 2017 | Kota, IN}
\sectionspace 

\section{LINKS} 

\href{https://github.com/sidowic}{Github}

\href{https://www.linkedin.com/in/siddhartha-nayak-9466441a9/}{LinkedIn}

\sectionspace 

\sectionspace 

\section{Coursework}


\sectionspace 

\subsection{Undergraduate}


Software Engineering \\
Programming Paradigms and Pragmatics \\
Computing & Data Structures \\
Theory of Computation \\
Computer Architecture \\
Computer Networks \\
Discrete Mathematical Structures \\ 



\sectionspace 

\section{Skills}

\subsection{Programming}
Over 15000 lines: \\
Python \textbullet{} JavaScript \textbullet{} Java \textbullet{} C \textbullet{} C++  \\
Over 5000 lines: \\
Latex \textbullet{} MySQL \textbullet{} RISC-V 

\sectionspace

\subsection{TECHNOLOGIES}
NodeJS \textbullet{} Git \textbullet{} Android
\sectionspace 


\end{minipage} 
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} 

\section{Project Experience}

\runsubsection{RISC-V ISA Simulator} |\descript{\small Dept. of Computer Science and Engineering, IIT ROPAR}

\location{Jan 2020 – May 2020}
\vspace{\topsep} 
\begin{tightitemize}
\item Designed and developed a simulator (with GUI) for RISC-V instruction set architecture..\\
\item Implemented both 5 stage pipelined and unpiplined execution.\\
\item Implemented Data Stalling, forwarding etc. for Data and Control
Hazards. 
\end{tightitemize}

\sectionspace 

\runsubsection{DBMS Project} |\descript{\small Dept. of Computer Science and Engineering, IIT ROPAR}

\location{July 2020 - Dec 2020 }
\begin{tightitemize}
\item We created an agent ticket booking platform for trains.
\item Here we have two login credentials one "agent" and other is "admin". The project was done using SQL language.
\end{tightitemize}

\sectionspace 


\runsubsection{Travel Reimbursement Form APP} |\descript{\small Dept. of Computer Science and Engineering, IIT ROPAR}

\location{Jan 2021 – May 2021}
\begin{tightitemize}
\item Designed and developed an easy to use travel reimbursement
application for schools and colleges using ReactJS and NodeJS.\\
\item App allows you to use store and download travel information.
\end{tightitemize}

\sectionspace 
 
\descript{mini projects}

\location{Jul 2018 - Current}
\textbullet{}Digital Logic Design Project | Language : Verilog\\
\textbullet{}Samskritam | our effort to help you learn Sanskirt : parent to all language


\sectionspace 

\section{Projects}
2021 | \location{Google Foobar}


\section{EXPERIENCES} 

\textbullet{}\location{\color{darkgray} Event Coordinator, Lifestyle Events}
{\footnotesize Zeitgeist - Annual Fest of IIT Ropar\\}
\textbullet{}\location{\color{darkgray} Club Member, Alankar, Arturo, Alpha}
{\footnotesize Music, Photography and Editing Club of IIT Ropar }
\sectionspace 

\end{minipage}

\end{document}