%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Ayushi}{Nayak}{ \urlstyle{same}\href{http://ayushinayak.in}{ayushinayak.com} | \href{mailto:hi@ayushinayak.in}{hi@ayushinayak.in} | (+353) 0899 879 258 | \href{mailto:d19123831@mytudublin.ie}{ayushi.nayak@tudublin.ie}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{TU Dublin}
\descript{MSc. in Computer Science}
\location{Jan 2021 | Dublin, IE}
\sectionsep

\subsection{BIJU PATNAIK UNIVERSITY OF TECHNOLOGY}
\descript{BTech. in Computer Science and Engineering}
\location{May 2016 | Bhubaneswar, IN}
College of Engineering and Technology \\
\location{ Cum. GPA: 8.27 / 10.0}
\sectionsep

\subsection{St. John's Senior Secondary School}
\location{May 2012 |  Kota, IN}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Facebook:// \href{https://www.facebook.com/ayushishradha}{\bf Ayushi Nayak} \\
Github:// \href{https://github.com/AyyNayak}{\bf Ayushi Nayak} \\
LinkedIn://  \href{https://www.linkedin.com/in/ayushinayak}{\bf Ayushi Nayak} \\
YouTube://  \href{https://www.youtube.com/channel/UCyy1Hf36JmKnh4T0i3I430w}{\bf Ayushi Nayak} \\
Twitter://  \href{https://twitter.com/Ayy_Nay}{\bf Ayushi Nayak} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
% skip system design and machine learning
Systems Architecture \\
Secure Systems Development \\
Web Applications Architecture \\
{\footnotesize \textit{\textbf{(Research Asst.) }}} \\
Programming Paradigms \\
Advanced Databases \\
Machine Learning \\
Deep Learning \\
Working with Data \\
\sectionsep

\subsection{Undergraduate}
Compiler Design \\ 
Theory of Computation  \\
Design and Analysis of Algorithm \\
Data Structures \\
Advanced Computer Architecture \\
Cryptography and Network Security \\
Data and Web Mining \\
Operating System \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Python \textbullet{} Javascript \textbullet{} Jupyter NB \textbullet{} \LaTeX\ \\ 
\location{Over 1000 lines:}
C \textbullet{} C++ \textbullet{} C Sharp  \textbullet{} Assembly  \textbullet{} Prolog\\
\location{Familiar:}
Go \textbullet{}   Java \textbullet{} iOS \textbullet{} Android \textbullet{} MySQL
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{TATA Consultancy Services Pvt. Ltd.}
\descript{| Systems Engineer }
\location{Mar 2017 - Study Sabbatical | Pune, In}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Led and shipped EV infra charging app – the mobile and Windows application for the new report generation system.
\item Full-stack Developer:  Wrote and reviewed code for Microsoft Z3 & Python using Django and Flask. Fixed UI bugs and upgraded backend to deploy over AWS.
\item Published research paper: Approach to Predict the Outcome of an EV Charger Getting Certiﬁed.
\item Received the Special Initiative award within three months of joining and an  On the Spot award from Nissan for quick project delivery.
\end{tightemize}
\sectionsep

\runsubsection{National Thermal Power Corp}
\descript{| Industrial Trainee }
\location{June 2015 – July 2015 | Mouda, India}
\begin{tightemize}
\item Worked on the most widely installed Customer Mailing System, in Python and JavaScript,  alongside Bodhtree.
\item Wrote a web application using a  Pylons framework to execute the revamped interface to view archives with improved search operations.
\end{tightemize}
\sectionsep

\runsubsection{Adani Power Maharashtra Ltd.}
\descript{| Vocational Trainee}
\location{June 2015 | Tirora, India}
\begin{tightemize}
\item IT network systems: learned to install, maintain, and manage networks and IT business systems.
\item Designed an MVP for the employment platform using C# and ASP .NET to match job providers and seekers, which offered voice interaction.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{School of Computer Science, TU Dublin}
\descript{| Research Assistant}
\location{Nov 2019 – Apr 2020 | Dublin, IE}
Worked with \textbf{\href{https://www.dit.ie/computing/people/academicstaff/staff/staffname161599en.html}{Sarah Jane Delaney}} to create \textbf{{HD-Intelligence}\href{https://hd-intelligence.com/}}, a tool to automate and facilitate the electronic discovery (e-discovery) process, including the identiﬁcation, preserving, collecting, processing, reviewing, analyzing, and producing digital data.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects} 
\begin{tabular}{rll}
2020	      & \href{https://github.com/GroupProjectSem3/Haley}{\bf Haley (ongoing)} \\
2020	     & \href{https://github.com/Yuce-Solutions/People-Counter-On-Edge}{\bf People Counter on Edge} \\
2020	     & \href{https://github.com/Yuce-Solutions/Smart_queueing_system_on_edge}{\bf Smart Queuing System on Edge} \\
\end{tabular}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2019 & 60/2500  & Centenary Scholarship Programme for TU Dublin Masters Students\\
2018 & - & TCS On the Spot award\\
2017 & - & TCS Special Initiative award\\
2012 & - & Adani Saraswati Sanman\\
2010 & 102/1.8 mil  & SSC Merit Scholarship\\
2008 & 13/10,000 & Vigyan Manthan Lifetime Merit Scholarship \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
\bibliographystyle{abbrv}
\bibliography{publications}
\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
